R dyntrace report

### 2018-04-03 graphs/report-main.Rmd
Sketch of specific analysis report.

``` {r, "basic info", include=FALSE}
aggregated_functions <- load_local_csv("aggregated_functions.csv") #

aggregated_functions %>% filter(!is.na(ERR1) || !is.na(ERR2)) %>% print

basic_info <- 
  load_local_csv("basic_info.csv") %>%
  group_by(name) %>%
  summarise(
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=sum(n.functions),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

top5_basic_info <- 
  basic_info %>% 
  arrange(desc(n.calls, n.promises, n.promise.accesses, n.functions))%>% head(5)

aggregate_basic_info <- 
  basic_info %>% summarise(
    name="*",
    datasets=paste(name, collapse=", "),
    n.datasets=n(),
    n.functions=(aggregated_functions %>% count %>% pull(n)),
    n.calls=sum(n.calls),
    n.promises=sum(n.promises),
    n.promise.forces=sum(n.promise.forces),
    n.promise.lookups=sum(n.promise.lookups), 
    n.alien.promises=sum(n.alien.promises),
    n.alien.promise.forces=sum(n.alien.promise.forces)
  )

missing_basic_info <- 
  basic_info %>% summarise(
    name="...",
    datasets="...",
    n.datasets="...",
    n.functions="...",
    n.calls="...",
    n.promises="...",
    n.promise.forces="...",
    n.promise.lookups="...", 
    n.alien.promises="...",
    n.alien.promise.forces="..."
  )

 n.packages <- basic_info %>% count %>% pull(n)

 # some graphical stuff
 package_figure_width <- 10
 package_figure_columns <- min(7, ceiling(sqrt(n.packages)))
 package_figure_rows <- ceiling(n.packages/package_figure_columns)
 package_figure_height <- ceiling(10/7 * package_figure_rows)
```

# Dataset

```{r, "dataset", echo=FALSE, comment="", row.names=FALSE}
basic_info %>% select(name) %>% distinct %>% pull(name) %>% as.character %>% print(row.names=FALSE)
```

<!--r path -->
# Overview

``` {r, "overview", echo=FALSE, warning=FALSE}
union(top5_basic_info, aggregate_basic_info) %>% 
  mutate(
    n.functions=pp_trunc(n.functions), 
    n.calls=pp_trunc(n.calls), 
    n.promises=pp_trunc(n.promises), 
    n.promise.accesses=pp_trunc(n.promise.forces + n.promise.lookups),
    n.promise.forces=pp_trunc(n.promise.forces),
    n.promise.lookups=pp_trunc(n.promise.lookups)
  ) %>% 
  select(name, n.functions, n.calls, n.promises, 
         n.promise.accesses, n.promise.forces, 
         n.promise.lookups) %>%  
  kable(col.names=c("package", "functions", "calls", "promises",
                    "promise accesses", "promise forces",
                    "promise lookups"), align="lrrrrrr")
```

<div style="font-size: 50%; padding-top: 2em">
**promise force** means the promise is accessed and the code of the promise is executed  
**promise lookup** mean the promise is accessed and the code of the promise is not executed
</div>

<!--div style="font-size: 50%;">
(showing top 5)
</div-->

<!--Alien promises are promises which were created before we began tracing. We don't have all the information regarding them, so we generally ignore them, including in the data below. They also are a subject of a lot of lookups in functions `from base::*`, which we don't record to save disk space.-->

# Promise accesses

```{r, "promise accesses", include=FALSE}
forces <- 
  load_local_csv("fuzzy_forces.csv") %>% 
  group_by(classification) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))
```

``` {r, "promise accesses kable", echo=FALSE}
forces %>% prettify %>% kable(col.names=c("classification","number","percentage"), align="lrr")
```

<!--``` {r evaluations-forces-graph, echo=FALSE, comment="", fig.width=10, fig.height=5}
ggplot(forces, aes(x="", y=percent, fill=classification)) + 
  geom_bar(width=1, stat="identity") + 
  #geom_text(aes(y=cumsum(percent)-percent/2, label=classification)) +
  coord_polar("y", start=0) +
  theme(legend.position="right", axis.title.y=element_blank())
```-->

<div style="font-size: 50%; padding-top: 2em">
**promise force** means the promise is accessed and the code of the promise is executed  
**promise lookup** mean the promise is accessed and the code of the promise is not executed
</div>

```{r, "promise accesses forces", include=FALSE}
forces <- 
  load_local_csv("fuzzy_forces.csv")

```

## Distribution per package

```{r, "promise accesses forces packages", echo=FALSE, fig.width=10, fig.height=3}
g_class <- function(x, y_axis=FALSE) {
    ggplot(forces %>% filter(classification==x), aes(x=classification, percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), legend.position="none") +
    ylab("percentage") +
    theme(axis.title.y=if (y_axis) element_text() else element_blank())
}

grid.arrange(
  g_class("accessed 2+ times, forced once", TRUE),
  g_class("accessed once, forced once"),
  g_class("accessed 1+ times, never forced"),
  g_class("never accessed"),
  ncol=4, widths=c(1.1,1,1,1))
```

# Number of accesses to a promise

## Aggregate

``` {r, "number of accesses to a promise, aggregate", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- 
  load_local_csv("promise_evaluations.csv") %>%
  group_by(no.of.evaluations) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  mutate(labels=no.of.evaluations) %>%
  mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
  mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
                                  max(no.of.evaluations, na.rm=TRUE)+1, 
                                  no.of.evaluations)) %>% 
  arrange(no.of.evaluations)

ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  scale_x_discrete(limit=0:11, labels=evaluations %>% pull(labels)) +
  theme(axis.title.x=element_blank(), legend.position="none") +
  ylab("No. of promises") + xlab("No. of accesses")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
</div>

## Distribution per package/vignette

``` {r, "number of accesses to a promise, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
evaluations <- load_local_csv("promise_evaluations.csv")
make_graphs_for_range(evaluations, "no.of.evaluations", max.col=6, f=function(data)
  ggplot(data, aes(x=no.of.evaluations, y=percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.position="none")
)
```

## Separate results per package/vignette

``` {r, "number of accesses to a promise, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
make_graphs_for_packages(load_local_csv("promise_evaluations.csv"), max.col=package_figure_columns, f=function(data) function(package) {
  evaluations <- 
    data %>% 
    filter(name == !!package) %>%
    mutate(percent=100*number/sum(number)) %>%
    mutate(labels=no.of.evaluations) %>%
    mutate(no.of.evaluations=as.numeric(as.character(no.of.evaluations))) %>% 
    mutate(no.of.evaluations=ifelse(is.na(no.of.evaluations), 
                                    max(no.of.evaluations, na.rm=TRUE)+1, 
                                    no.of.evaluations))

  evaluations <- 
    tibble(no.of.evaluations=c(0:11)) %>% 
    left_join(evaluations, by="no.of.evaluations") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(evaluations, aes(x=no.of.evaluations, y=number)) + 
    geom_col() +
    scale_x_discrete(limit=0:11, labels=c(0:10,">10")) +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(evaluations, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Promise code types

## Aggregate

``` {r, "promise code types, aggregate", echo=FALSE, fig.width=10, fig.height=5}
promise_types <- 
  load_local_csv("promise_types.csv")

ggplot(promise_types %>% group_by(type) %>% summarise(number=sum(number)) %>% mutate(percent=100*number/sum(number)), 
       aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5)) +
  ylab("No. of promises") + 
  xlab("Promise type")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
<!--**α→β** indicates that type **α** variously evaluates to type **β**.
**α** indicates that the promise contains the expression of type **α**.  
**→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.
**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.  
**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  -->
</div>

## Distribution per package/vignette

``` {r, "promise code types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(promise_types, "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) +
    geom_violin(draw_quantiles = c(.25, .5, .75)) +
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(), 
          axis.title.y=element_blank(), 
          legend.position="none")
)
```

## Separate results per package/vignette

``` {r, "promise code types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
available_sexps <- promise_types %>% select(type) %>% distinct %>% pull(type)

make_graphs_for_packages(promise_types, max.col=package_figure_columns, f=function(data) function(package) {
  promise_types <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  promise_types <- 
    tibble(type=available_sexps) %>% 
    left_join(promise_types, by="type") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(promise_types, aes(x=type, y=number)) + 
    geom_col() +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Type traces

```{r, "what's inside promises", echo=FALSE, fig.width=10, fig.height=4.5}
promise_full_types <-
  load_local_csv("promise_full_types.csv") %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>% 
  mutate(type=as.character(type)) #%>%
  #filter(grepl("^PROM", type)) %>%
  #mutate(type=gsub("PROM", "", type))
  #mutate(type=ifelse(len(type) > 15, paste0(strtrim(type, 13), ".."), type))

promise_full_types %>% 
  arrange(desc(number)) %>%
  mutate(number=pp_trunc(number), percent=pp_perc(percent)) %>%
  select(number, percent, type) %>%
  kable(col.names=c("number", "percent", "type trace"), align="lll")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
<!--**α→β** indicates that type **α** variously evaluates to type **β**.  -->
**α** indicates that the promise contains the expression of type **α**.  
**PROM→α** indicates that the promise contains a promise which contains the expression of type **α**, etc.  
**BCODE →α** indicates that it's a byte-compiled expression that was originally of type **α**.    
**SYM→α** indicates that it's a symbol that points to an expression of type **α**.  
**...** is a type that could not has not been correctly determined.
</div>

# Promise return types

## Aggregate

``` {r, "promise return types, aggregate",  echo=FALSE, fig.width=10, fig.height=5}
return_types <- 
  load_local_csv("return_types.csv")

ggplot(return_types %>%   
         group_by(type) %>% 
         summarise(number=sum(number)) %>% 
         mutate(percent=100*number/sum(number)), 
       aes(x=type, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Return type")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
</div>

## Distribution per package/vignette

``` {r, "promise return types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
#make_graphs_for_range(return_types, "type", max.col=5, f=function(data)
#  ggplot(data, aes(x=type, y=percent)) +
#    geom_violin(draw_quantiles = c(.25, .5, .75)) +
#    scale_y_continuous(labels=pp_perc) +
#    theme(axis.title.x=element_blank(), 
#          axis.title.y=element_blank(), 
#          legend.position="none")
#)
```

## Separate results per package/vignette

``` {r, "promise return types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
available_sexps <- return_types %>% select(type) %>% distinct %>% pull(type)

make_graphs_for_packages(return_types, max.col=package_figure_columns, f=function(data) function(package) {
  promise_types <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  promise_types <- 
    tibble(type=available_sexps) %>% 
    left_join(promise_types, by="type") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(promise_types, aes(x=type, y=number)) + 
    geom_col() +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(promise_types, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

## What do specific promises return?

```{r, "what do specific promises return", echo=FALSE, comment="", fig.width=10.5, fig.height=4.5}
types_to_return_types <- 
  load_local_csv("promise_code_to_return_types.csv") %>%
  group_by(types) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number)) %>%
  arrange(desc(number))

ggplot(types_to_return_types, aes(x=types, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank(),
        legend.position="none", 
        axis.text.x=element_text(angle=90, vjust=.5, hjust=1)) +
  ylab("No. of promises") + 
  xlab("Type/return type")
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.  
**α→β** indicates that the promise contains an expression of type **α** which evaluates to  an expression of type **β** when the promise is forced.
</div>

# Promise forces by types

## Aggregate

```{r, "promise forces by types, aggregate",  echo=FALSE, , comment="", fig.width=10, fig.height=5}
force.histogram.by.type <- load_local_csv("forces_by_type.csv")

ggplot(
  force.histogram.by.type %>%
    group_by(type, no.of.forces) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number)), 
  aes(x=type, y=number, fill=factor(no.of.forces))) + 
geom_bar(stat="identity", position="dodge") +
ylab("No. of promises") + 
scale_fill_discrete(name="No. of forces",
                    breaks=(force.histogram.by.type$no.of.forces %>% unique),
                    labels=(force.histogram.by.type$no.of.forces %>% unique)) +
scale_y_continuous(labels=pp_trunc) +
theme(axis.title.x=element_blank(), legend.position = c(0.9, 0.9))
```

<div style="font-size: 50%">
Promise types follow the type designations in ``Rinternals.h``.
</div>

## Distribution per package

```{r, "promise forces by types, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}

types <- force.histogram.by.type %>% pull(type) %>% unique
forces <- force.histogram.by.type %>% pull(no.of.forces) %>% unique
featured_packages <- force.histogram.by.type %>% pull(name) %>% unique

force_histogram_filled_in <- 
  expand.grid(type=types, no.of.forces=forces, name=featured_packages) %>%
  left_join(force.histogram.by.type, by=c("type", "no.of.forces", "name")) %>%
  mutate(number=ifelse(is.na(number), 0, number),
         percent=ifelse(is.na(percent_overall), 0, percent_overall)) %>%
  mutate(forces=paste0(type, "/", no.of.forces)) %>%
  #select(forces, number, percent, name) %>% 
  arrange(forces) %>% 
  as_tibble

make_graphs_for_range(force_histogram_filled_in, "forces", max.col=5,
  f=function(data) 
    ggplot(data, aes(x=forces, y=percent)) +
    geom_violin() +
    #geom_violin(draw_quantiles=c(.25, .5, .75)) + # this one errors out and idk why
    scale_y_continuous(labels=pp_perc) +
    theme(axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          legend.position="none")
)
```

## Separate results per package/vignette

``` {r, "promise forces by types, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
#type_range <- force_histogram_filled_in %>% select(type) %>% distinct %>% pull(forces)

make_graphs_for_packages(force_histogram_filled_in, max.col=package_figure_columns, f=function(data) function(package) {
  force_histogram <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type, no.of.forces) %>% 
      summarise(number=sum(number)) %>% 
      mutate(percent=100*number/sum(number))
    #group_by(type) %>% summarise(number=sum(number)) %>% 
    #mutate(percent=100*number/sum(number))

  ggplot(
    force_histogram,
    aes(x=type, y=number, fill=factor(no.of.forces))) + 
    geom_bar(stat="identity", position="dodge") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(pull(force_histogram, number)))) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.ticks.y=element_blank(),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Promise evaluation distances

## Aggregate

<!--Effective distance is the distance from the call where a promise originated to the call in which it was evaluated. It is measured along the call graph (along inbound edges).  Since the data is gathered from a trace, the call graph is a tree.-->

```{r, "promise actual distances, aggregate", echo=FALSE, fig.width=10, fig.height=4.5}
actual_distances <- load_local_csv("actual_distances.csv")

ggplot(actual_distances %>% 
         group_by(actual_distance) %>% 
         summarise(number=sum(number, na.rm=TRUE)) %>% 
         mutate(percent=100*number/sum(number)), aes(x=actual_distance, y=number)) + 
  geom_col() +
  scale_x_discrete(limits=c(NA,0:20,">20",-1)) +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  theme(axis.title.x=element_blank())
```

<div style="font-size: 50%">
**n** - distance from the function for which a promise was created and the function in which it was evaluated    
**NA** - promise was not executed, there is no distance measure (a virgin promise)  
**-1** - promise was executed but there is no path from the origin to the point of evaluation (an escaped promise)    
</div>

## Distribution per package/vignette

``` {r, "promise actual distances, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=7}
make_graphs_for_range(actual_distances %>%
  mutate(actual_distance = ifelse(is.na(actual_distance), "NA", actual_distance)),
  "actual_distance", max.col=5, f=function(data)
  ggplot(data, aes(x=actual_distance, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Separate results per package/vignette

``` {r, "promise evaluation distance, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- actual_distances %>% select(actual_distance) %>% distinct %>% pull(actual_distance)

make_graphs_for_packages(actual_distances, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(actual_distance) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(actual_distance=range) %>% 
    left_join(package_data, by="actual_distance") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=actual_distance, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Calls and functions by type

## Aggregate

<center>
<div class="col2">
<div class="together">
```{r, "calls by type", echo=FALSE, fig.width=5, fig.height=4}
calls_types <- load_local_csv("call_types.csv")

data <- 
  calls_types %>% 
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=type, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of calls") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```
</div>

```{r, "functions by type", echo=FALSE, fig.width=5, fig.height=4}
function_types <- load_local_csv("aggregated_function_types.csv")

data <- function_types %>%
  group_by(type) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=type, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of function definitions") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```
</div>
</center>

<div style="font-size: 50%">
**functions** refers to function definitions   
**calls** refers to function executions/calls
</div>

## Calls by type, distribution per package/vignette

``` {r, "calls by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(calls_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Functions by type, distribution per package/vignette

``` {r, "functions by type, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(function_types %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "type", max.col=5, f=function(data)
  ggplot(data, aes(x=type, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Calls by type, separate results per package/vignette

``` {r, "calls by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- calls_types %>% select(type) %>% distinct %>% pull(type)
make_graphs_for_packages(calls_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(type=range) %>% 
    left_join(package_data, by="type") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=type, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

## Functions by type, separate results per package/vignette

``` {r, "functions by type, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- function_types %>% select(type) %>% distinct %>% pull(type)
make_graphs_for_packages(function_types, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(type) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(type=range) %>% 
    left_join(package_data, by="type") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=type, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Byte-code compilation

## Aggregate

<center>
<div class="col2">
<div class="together">
```{r, "byte-code compilation, calls", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_call_compilation <- load_local_csv("compiled_calls.csv")

data <- 
  closure_call_compilation %>% 
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=compiled, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of calls") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```
</div>

```{r, "byte-code compilation, functions", echo=FALSE, fig.width=5, fig.height=3.5, warning=FALSE}
closure_function_compilation <- load_local_csv("aggregated_compiled_functions.csv")

data <- 
  closure_function_compilation %>% 
  group_by(compiled) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

ggplot(data, aes(x=compiled, y=number)) + 
  geom_bar(stat="identity") +
  ylab("No. of calls") + 
  scale_y_continuous(labels=pp_trunc) +
  theme(axis.title.x=element_blank())
```

```{r, "byte-code compilation, functions loading", echo=FALSE, warning=FALSE}
closure_function_compilation <- load_local_csv("compiled_functions.csv")
```

</div>
</center>

<div style="font-size: 50%">
When calling a function it's either byte-code **compiled** or **uncompiled**. When agregated across all calls to a function, a function can be:  
**compiled** - all calls to this function are compiled,  
**uncompiled** - none of the calls to this function are compiled,  
**after 1st** - a function can be compiled by the JIT, so it can be uncompiled initially and then compiled later on,  
**erratic** - a function is sometimes compiled and sometimes not; it can indicate that two separate functions are indistinguishable to the tracer (same definition, unknown location) and one of them is compiled while another is not.
</div>

## Compiled calls, distribution per package/vignette

``` {r, "byte-code compilation, calls, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(closure_call_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "compiled", max.col=5, f=function(data)
  ggplot(data, aes(x=compiled, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Compiled functions, distribution per package/vignette

``` {r, "byte-code compilation, functions, per package", echo=FALSE, warning=FALSE, fig.width=10, fig.height=5}
make_graphs_for_range(closure_function_compilation %>% mutate(percent = ifelse(is.na(percent), 0, percent)),
  "compiled", max.col=5, f=function(data)
  ggplot(data, aes(x=compiled, y=percent)) + 
  geom_violin() +
  scale_y_continuous(labels=pp_perc) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        legend.position="none")
)
```

## Compiled calls, separate results per package/vignette

``` {r, "compiled calls, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- closure_call_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
make_graphs_for_packages(closure_call_compilation, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(compiled) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(compiled=range) %>% 
    left_join(package_data, by="compiled") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=compiled, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

## Compiled functions, separate results per package/vignette

``` {r, "compiled functions, separate per package", echo=FALSE, warning=FALSE, fig.width=package_figure_width, fig.height=package_figure_height}
range <- closure_function_compilation %>% select(compiled) %>% distinct %>% pull(compiled)
make_graphs_for_packages(closure_function_compilation, max.col=package_figure_columns, f=function(data) function(package) {
  package_data <- 
    data %>% 
    filter(name == !!package) %>%
    group_by(compiled) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number))

  package_data <- 
    tibble(compiled=range) %>% 
    left_join(package_data, by="compiled") %>%
    mutate(
      number=ifelse(is.na(number), 0, number),
      percent=ifelse(is.na(percent), 0, percent))

  ggplot(package_data, aes(x=compiled, y=number)) + 
    geom_bar(stat="identity") +
    scale_y_continuous(labels=pp_trunc, breaks=c(max(package_data$number))) +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.text.y=element_text(angle=90, size=5, vjust=.5),
          axis.text.x=element_text(angle=90, size=5, vjust=.5),
          axis.title.x=element_text(size=5),
          legend.position="none") +
    xlab(package)
})
```

# Interactions among promises

```{r, "interactions among poromises", echo=FALSE, comment="", fig.width=10, fig.height=4.5}
# Graph one
promises_forced_by_another_promise <-   
  load_local_csv("promises_forced_by_another_promise.csv")

g_receive <- 
  ggplot(promises_forced_by_another_promise %>% 
    group_by(forced_by_another) %>% 
    summarise(number=sum(number)) %>% 
    mutate(percent=100*number/sum(number)), 
  aes(x=forced_by_another, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  theme(legend.position="none") +
  ylab("No. of promises") + 
  xlab("This promise forced\nby another promise")

# Graphs two and three
promises_forcing_other_promises <- 
  load_local_csv("promises_forcing_other_promises.csv")

promises_forcing_other_promises_summarized <- 
  promises_forcing_other_promises %>%
  group_by(number_of_forced_promises) %>% 
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

# Graph two
promises_forcing_other_promises_small <-
  promises_forcing_other_promises_summarized %>% 
  mutate(number_of_forced_promises=ifelse(number_of_forced_promises>=3, "3+", 
                                          number_of_forced_promises)) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

g_cause_small <- 
  ggplot(promises_forcing_other_promises_small, aes(x=number_of_forced_promises, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  xlab("No. of promises forced\nby this promise") +
  theme(legend.position="none", axis.title.y=element_blank())

# Graph three
promises_forcing_other_promises_big <-
  promises_forcing_other_promises_summarized %>% 
  filter(number_of_forced_promises >= 3) %>%
  group_by(number_of_forced_promises) %>%
  summarise(number=sum(number)) %>% 
  mutate(percent=100*number/sum(number))

g_cause_big <- 
  ggplot(promises_forcing_other_promises_big, aes(x=number_of_forced_promises, y=number)) + 
  geom_col() +
  scale_y_continuous(labels=pp_trunc) +
  ylab("No. of promises") + 
  xlab("No. of promises forced\nby this promise (3+)") +
  theme(legend.position="none", axis.title.y=element_blank())

# Drawing
grid.arrange(g_receive, g_cause_small, g_cause_big, ncol=3, widths=c(4,5,9))
```

>>>>

```{r child = 'report-basic-info.Rmd'}
```
